%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
{Software Engineer} % Job title
{Gorillas} % Organization
{Berlin, Germany} % Location
{July. 2021 - Present} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Implemented and owned a core domain that resulted in reduction of under utilised riders}
    \item {Worked with a data team to drastically improved the accuracy of ETAs within our system}
    \item {Implementing microservices for key business domains using Domain Driven Design}
    \item {Worked on Decomposing a monolithic service into decoupled cohesive microservices}
    \item {Involved with evaluating and hiring Backend Engineering candidates}
    \item {Assisting and mentoring Junior engineers}
  \end{cvitems}
}

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Ströer SSP Gmbh} % Organization
    {Berlin, Germany} % Location
    {Jun. 2019 - Jun. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented and configured Load Balancers to handle 100k/s requests for Core service using Haproxy and Nginx resulting in smoother peak performance.}
        \item {Provisioned hybrid infrastructure(Amazon AWS + On-premise) utilizing IaC(Infrastructure as Code) tools like Puppet and Terraform.}
        \item {Built fully automated CI/CD pipelines with modern Gitops technology(Fluxcd, Jenkins, docker) for several Core services.}
        \item {Deployed a centralized monitoring environment(Grafana, Prometheus) which gather system metrics as well as docker run-time metrics.}
        \item {Administered and maintained Kubernetes Clusters and on premise Bare Metal Machines.}
        \item {Migrated Several Key Services from legacy debian packages to docker and kubernetes.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Joblift Gmbh} % Organization
    {Berlin, Germany} % Location
    {Aug. 2018 - Jun. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Automated Operation workflows that minimized menial work for the operations team.}
        \item {Worked emailing templates that resulted in improved user signup.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Business Intelligence Intern} % Job title
    {Joblift Gmbh} % Organization
    {Berlin, Germany} % Location
    {Feb. 2018 - Aug 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed automation infrastructure that allowed smooth and automatic collection and integration into the KPI report for accurate real-time reporting.}
        \item {Developed APIs for several partners that allowed for automatic data retrieval.}
        \item {Responsible for generating partner dashboards; These reports lead to the sales of new customers and customer retention.}
        \item {Performing AB test analysis on new product trials to verify to the efficacy.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Student} % Job title
    {UNSW BlueSat} % Organization
    {Sydney, Australia} % Location
    {Jan. 2017 - Nov 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Enabled wheel alignment software for the Rover that allowed for wheel calibration on start up.}
      \end{cvitems}
    }


%---------------------------------------------------------
\end{cventries}
